---
title: "Exercise 3.11"
author: "Anna Cook"
date: "2/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Exercise 3.11

In this exercise, we are comparing two types of aspirin. For the original aspirin, the probability of curing a headache is 0.6, while the other is predicted to be an improvement. Therefore, the null hypothesis is that the two aspirins are equal is ability to cure a headache. The alternative hypothesis is that the new aspirin's probability to improve a headache is > 0.6. If this is tested on 100 individuals, we want to determine the number of people who need to report a cured headache with the new aspirin in order to confirm that the new aspirin is an improvement on the old one. We want both the type 1 and type 2 errors to be less than 5%. 

First, we determine the critical values by finding the "cutoff" points where the type 1 and type 2 values are less than 0.05. The R code for this step is shown below. 

```{r}
# initial set up
n <- 100
p0 <- 0.6
p1 <- 0.8

# find lower critical value
for (i in 0:n) {
  alpha <- 1 - pbinom(i, n, p0)
  if (alpha < 0.05) break
}
m0 <- i
m0

# find upper critical value
for (i in 0:n) {
  beta <- pbinom(i, n, p1)
  if (beta > 0.05) break
}
m1 <- i
m1
```


These critical values confirm the results presented in the textbook. The next step is to replicate the power curves shown in figure 3.7. To do this, we need to create both power curves, one for the lower critical value and one for the upper critical value. Then, we must plot both curves on one graph and include a box outlining the probabilities as well as the cutoff points for 0.05 and 0.95 to show where the errors are unlikely to occur. The R code and output is shown below.

```{r}
# create power curve for m = 68
pwr1 <- cumsum(dbinom(m0, 100, prob = seq(from = 0, to = 1, by = 0.01)))
plot(pwr1, type = "l")

# create power curve for m = 73
pwr2 <- cumsum(dbinom(m1, 100, prob = seq(from = 0, to = 1, by = 0.01)))

# plot both curves together with box
plot(pwr2, type = "l", ylab = "power", xlim = c(40,100), ylim = c(0,1))
lines(pwr1, type = "l", xlab = "probability * 100")
segments(60, 0.05, 80, 0.05)
segments(60, 0.05, 60, 0.95)
segments(60, 0.95, 80, 0.95)
segments(80, 0.95, 80, 0.05)

```

From this graph we can see that the two power curves enclose all of the values for the number of people whose headaches must be cured in order for the new aspirin to be confirmed as more effective, while still keeping the type 1 and 2 errors below 5%. If the power curves were to the right or left of the two on this plot, that would indicate that one error or the other would be greater than 5%. 
